Income Has Serious Implications On Many Facets of American Life in 2021

### 2022-03-21 outputs/paper/paper.Rmd
6th commit

---
title: "Income Has Serious Implications On Many Facets of American Life in 2021"
subtitle: "A Look Into The Implications of Americans' Incomes Reveals Information On The Veracity of American Dream."
author: 
  - Adam Labas  
  - Krupali Bhavsar
thanks: "Code and data are available at: XXXXXXXXXXXXXXXXXXXXXXX"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: TRUE
bibliography: references.bib
---

@@

@@

We would like to contrast this with the current income of responds. The below is the same graph above but we've also included a similar graph but for family income at the time of response 
```{r figure2, fig.cap="write a figure caption here", echo = FALSE, fig.width=12, fig.height=10, message = F, warning = F}
#income16 vs income grouped by gender

@@

## Implications 1
In Visuals \@ref(visual-1) we can see when we look into income16 that the majority of people claimed that at the age of 16, their family income was over 40 thousand dollars. When we lookover at the income variable, we are trully perplexed to see that the largest is 25 thousand or more. We will discuss the implications of the latter in Section \@ref(limitations). We can also see that the number of NA responses rises from about 530 in the case of the income at age 16 variable to approximately 900 in the income variable. This seems counter intuitive as it would appear that less people are uncertain about their family income at age 16 than they are. We suspect however that this is not true. We suspect that there could be a possible shame or embarassment assosociated with sharing ones current faily income as it represents the persons way of living or lifestyle today. On the other hand, someones incomeat age 16 is psychologically less of importance to them and carries no burden in their life, as it is notan expected metric of succes year down the line. We also recognize that amongst men and women, there is a general

@@

```{r, fig.cap="write a figure caption here", echo = FALSE, fig.width=9, fig.height=6, message = F, warning = F}
#income at 16 vs current income grouped by where individual was born

income_income16_born <- ggplot(mapping = aes(x = income_cat, y = income16_cat, color = born), data = reduced_data) +
  geom_point() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x = "Current Family Income",
       y = "Family Income at Age 16",
       color = "Born in The USA",
       title = "Relationship Between Family Income at age 16 and Current Family Income")

income_income16_born
```

@@

# Additional details

>>>>

---
title: "Income Has Serious Implications On Many Facets of American Life in 2021"
subtitle: "A Look Into The Implications of Americans' Incomes Reveals Information On The Veracity of American Dream."
author: 
  - Adam Labas  
  - Krupali Bhavsar
thanks: "Code and data are available at: https://github.com/adam-labas/The-US-GSS-And-The-American-Dream"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: TRUE
bibliography: references.bib
---

@@

{ width="800" height="600" style="display: block; margin: 0 auto" }

@@

We would like to contrast this with the current income of responds. The below is the same graph above but we've also included a similar graph but for family income at the time of response.
```{r figure2, fig.cap="write a figure caption here", echo = FALSE, fig.width=12, fig.height=10, message = F, warning = F}
#income16 vs income grouped by gender

@@

## Implications 1
In Visuals \@ref(visual-1) we can see when we look into income16 that the majority of people claimed that at the age of 16, their family income was over 40 thousand dollars. When we look over at the income variable, we are truly perplexed to see that the largest is 25 thousand or more. We will discuss the implications of the latter in Section \@ref(limitations). We can also see that the number of NA responses rises from about 530 in the case of the income at age 16 variable to approximately 900 in the income variable. This seems counter intuitive as it would appear that less people are uncertain about their family income at age 16 than they are. We suspect however that this is not true. We suspect that there could be a possible shame or embarrassment associated with sharing ones current family income as it represents the persons way of living or lifestyle today. When we speak of the American dream, we implicitly assume an increase in wealth over time and for someone who isn't as wealthy as they might want to be (likely an overwhelming large portion of the population), reluctance with sharing their current income is totally understandable. On the other hand, someones income at age 16 is psychologically less of importance to them and carries no burden in their life, as it is not an expected metric of success years down the line. We also recognize that among men and women, there is a general almost a 50:50 split at each level of income but we do notice that for income level NA, a lot of people chose not to identify their gender. It would be interesting in another analysis to analyse possible evidences of gender pay gap and how people who do not fit in the *traditional* gender roles are affected by the advent of the American Dream and whether or not their position in life hinders their ability to increse in wealth over time.

As we speak about an increase in wealth over time, we next want to see if the birth place of ones grandparents has any impact on income due to the so called *generational wealth*.

## Visual 2
As weve previously stated, the American
\@ref(visual-2)

@@

@@
